---
title: 'Project Modeling with Classification Trees'
author: "Joshua Ambrose"
date: "9/19/2020"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rpart)
library(rpart.plot)
```

### Summary
Summary of the data used for this project. PRODUCT is removed as a predictor for this project since it records an event that takes place after the outcome. ANSWERED, FEMALE, JOB, RENT, OWN_RES, NEW_CAR, MOBILE were converted to factors.
```{r cleaned, echo=FALSE}
data_unclean <- read.csv("C:/Users/joshua.ambrose/Downloads/adviseinvest_clean.csv")
data <- data_unclean
drop <- c("product")
data <- data[ , !(names(data) %in% drop)]

data$answered <- factor(data$answered)
data$female <- factor(data$female)
data$job <- factor(data$job)
data$rent <- factor(data$rent)
data$own_res <- factor(data$own_res)
data$mobile <- factor(data$mobile)
summary(data)
```
### Proportion of Answered Calls
This is the proportion of answered calls for question one. Since the data is binary where 0 indicates unanswered and 1 indicates answered, the mean is the average of answered calls.
```{r proportion, echo=T}
summary(data_unclean$answered)
```
### Income Model
The below defined income model has an accuracy of 0.648.

```{r income model, echo=T}
income_model <- rpart(answered ~ income, data = data)
rpart.plot(income_model)

(predict(income_model, type = "class") == data$answered) %>% 
  mean
```

### Information Gain
IG(parent,children)=entropy(parent)−[p(c1)entropy(c1)+p(c2)entropy(c2)+...]

The calculations used to get IG, and IG itself, are shown below:

```{r information gain, echo=T}
income_model

entropy_parent <- -0.4570000 * log2(0.4570000) - 0.5430000 * log2(0.5430000)
print(entropy_parent)
pc1 <- 1385/5000
print(pc1)
pc2 = 1 - pc1
print(pc2)
entropyc1 = -0.3574007 * log2(0.3574007) - 0.6425993 * log2(0.6425993)
print(entropyc1)
entropyc2 = -0.3858921  * log2(0.3858921 ) - 0.6141079 * log2(0.6141079)
print(entropyc2)

IG <- entropy_parent - (pc1 * entropyc1 + pc2 * entropyc2)
print(IG)

```
### Tree Model
The below defined tree model has an accuracy of 0.8104.

```{r tree model, echo=T}
tree_model <- rpart(answered ~ ., data = data)
rpart.plot(tree_model)

(predict(tree_model, type = "class") == data$answered) %>% 
  mean
```